---
title: "session 6 practice"
author: "Maria Prokofieva"
date: "21/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Hotel bookings dataset

Today we are working with `hotel bookings` dataset from [TidyTuesday project](https://github.com/rfordatascience/tidytuesday/tree/master/data/2020/2020-02-11)

We are going to use core functions from [`tidyverse`](https://www.tidyverse.org/packages/#core-tidyverse)

Let's load libraries 

```{r}
library(tidyverse)
library(skimr)
```

and loading the dataset `hotel bookings` using the description at the `github` page

```{r}
hotels <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv')

head(hotels)
```

Let's explore the dataset
```{r}

hotels %>%skim()

hotels%>%distinct(hotel)

hotels%>%count(hotel)

hotels%>%count(arrival_date_year)

```

Let's do some data transformation as discussed in the class:

```{r}
hotels%>%
  mutate(arrival_date_year=as_factor(arrival_date_year))%>%
  group_by(arrival_date_year)%>%
  count(is_canceled, sort=TRUE)%>%
  ungroup()


hotels%>%
  group_by(hotel)%>%
  mutate(average_lead_time=mean(lead_time))%>%
  ungroup()
  
hotels%>%head()
```

How is this different from? Why? What changed?

```{r eval=FALSE}
hotels%>%
 # group_by(hotel)%>%
  mutate(average_lead_time=mean(lead_time))%>%
 # ungroup()
  
hotels%>%head()
```

What does it show us?

How is this different from? What changed?

```{r}
hotels%>%
  group_by(hotel)%>%
  mutate(m_lead_time=max(lead_time))%>%
  ungroup()
  
hotels%>%head()
```

How is this different if we use `summarise`?

Average number of days in `lead_time` per type of hotel

```{r}
hotels%>%
  group_by(hotel)%>%
  summarise(average_lead_time=mean(lead_time))%>%
  ungroup()
```

Data viz of cancellations per type of hotel

```{r}
hotels%>%ggplot(
  aes(is_canceled)
)+
  geom_bar()+
  facet_wrap(vars(hotel))

```

Calculate the maximum `lead_time`

```{r}

hotels%>%
  group_by(hotel)%>%
  mutate(max_lead_time=max(lead_time))%>%
  filter(hotel=="City Hotel")%>%
  select (hotel, max_lead_time)%>%
  ungroup()

```

How can we plot number of adults (`adults`) against number of days in weekends bookeed?

```{r}
hotels %>%
  ggplot(
    aes(x=adults, y=stays_in_weekend_nights))+
  geom_point()
```

What does this tell us about data?



