---
title: "Session 9"
author: "Maria Prokofieva"
date: "18/05/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)
library(scales)
theme_set(theme_light())
```

# Decision Trees

A decision tree is a decision support tool that uses a tree-like model of decisions and their possible consequences, including chance event outcomes, resource costs, and utility. It is one way to display an algorithm that only contains conditional control statements.

Decision trees can be learned from training data. Training data will typically comprise many instances of the following kind:

Instance 1	attribute1	attribute2	...	attributeK	class
Instance 2	attribute1	attribute2	...	attributeK	class
The decision tree learning algorithm recursively learns the tree as follows:

Assign all training instances to the root of the tree. Set curent node to root node.

For each attribute

- Partition all data instances at the node by the value of the attribute.

- Compute the information gain ratio from the partitioning.

- Identify feature that results in the greatest information gain ratio. Set this feature to be the splitting criterion at the current node.

- If the best information gain ratio is 0, tag the current node as a leaf and return.

- Partition all instances according to attribute value of the best feature.

- Denote each partition as a child node of the current node.

- For each child node:

-If the child node is “pure” (has instances from only one class) tag it as a leaf and return.

-If not set the child node as the current node and recurse to step 2.


## Load the weekly Data

Dowload the weekly data and make available in the `tt` object.


```{r}
ikea <-readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-11-03/ikea.csv') %>%
  select(-X1) %>%
  mutate(price_usd = 0.27 * price,
         short_description = str_squish(short_description)) %>%
  add_count(category, name = "category_total")
ikea %>%
  count(category, sort = TRUE) %>%
  mutate(category = fct_reorder(category, n)) %>%
  ggplot(aes(n, category)) +
  geom_col() +
  labs(x = "# of items",
       y = "",
       title = "Most common categories of IKEA items")
```

```{r}
library(glue)
ikea %>%
  mutate(category = glue("{ category } ({ category_total })"),
         category = fct_reorder(category, price_usd)) %>%
  ggplot(aes(price_usd, category)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1, alpha = .25) +
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

```{r}
library(ggridges)
ikea %>%
  mutate(category = glue("{ category } ({ category_total })"),
         category = fct_reorder(category, price_usd)) %>%
  ggplot(aes(price_usd, category)) +
  geom_density_ridges() +
  # geom_jitter(width = 0, height = .1, alpha = .25) +
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

```{r}
ikea %>%
  mutate(category = glue("{ category } ({ category_total })"),
         category = fct_reorder(category, price_usd)) %>%
  ggplot(aes(price_usd, category, fill = other_colors)) +
  geom_density_ridges(alpha = .5) +
  # geom_jitter(width = 0, height = .1, alpha = .25) +
  scale_x_log10(labels = dollar) +
  labs(x = "Price (USD)",
       y = "",
       title = "How much do items in each category cost?")
```

If we were building a predictive model, we'd probably include both category and other_colors

```{r}
ikea %>%
  mutate(name = fct_lump(name, 20)) %>%
  filter(name != "Other") %>%
  count(name, category, sort = TRUE) %>%
  mutate(name = fct_reorder(name, n, sum),
         category = fct_reorder(category, n, sum)) %>%
  ggplot(aes(n, name, fill = category)) +
  geom_col() +
  scale_fill_discrete(guide = guide_legend(reverse = TRUE)) +
  labs(x = "# of items",
       y = "Name of item")
```

```{r}
ikea %>%
  separate(short_description,
           c("main_description", "rest"),
           sep = ", ",
           extra = "merge",
           fill = "right",
           remove = FALSE) %>%
  extract(rest, "description_cm", "([\\d\\-xX]+) cm", remove = FALSE) %>%
  unite(category_and_description, category, main_description, sep = " - ") %>%
  count(category_and_description, sort = TRUE)
```

### Volume

```{r}
ikea_volume <- ikea %>%
  mutate(volume_m3 = depth * height * width / 1e6) %>%
  filter(!is.na(volume_m3),
         volume_m3 >= .001) %>%
  arrange(desc(volume_m3)) %>%
  add_count(category, name = "category_total")
ikea_volume %>%
  arrange(desc(volume_m3))
ikea_volume %>%
  mutate(category = glue("{ category } ({ category_total })"),
         category = fct_reorder(category, volume_m3)) %>%
  ggplot(aes(volume_m3, category)) +
  geom_boxplot() +
  # geom_jitter(width = 0, height = .1, alpha = .25) +
  scale_x_log10() +
  labs(x = "Volume of furniture (cubic meters)",
       y = "",
       title = "How much space do items in each category take up?")
```

What is the highest "price per cubic meter"?

```{r}
ikea_volume %>%
  mutate(category = fct_lump(category, 6)) %>%
  ggplot(aes(volume_m3, price_usd, color = category)) +
  geom_point() +
  geom_smooth(method = "lm") +
  scale_x_log10() +
  scale_y_log10()
ikea_volume %>%
  mutate(dollar_per_m3 = price_usd / volume_m3) %>%
  arrange(desc(dollar_per_m3)) %>%
  View()
```

```{r}
ikea %>%
  group_by(designer) %>%
  summarize(n_items = n(),
            n_names = n_distinct(name),
            n_category = n_distinct(category)) %>%
  arrange(desc(n_names))
```

```{r}
library(broom)
ikea_volume %>%
  mutate(category = fct_relevel(category, "Tables & desks")) %>%
  lm(log2(price_usd) ~ log2(volume_m3) + category + other_colors, data = .) %>%
  tidy(conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(term = ifelse(term == "log2(volume_m3)", "Item volume (doubling)", term),
         term = str_remove(term, "^category")) %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(estimate, term)) +
  geom_point() +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = .1) +
  geom_vline(xintercept = 0, color = "red", lty = 2) +
  labs(x = "Impact on price (relative to Tables & desks)",
       y = "",
       title = "What objects are unusually expensive/inexpensive relative to volume?")
```
